---
title: "Assignment 2"
author: "Sri Sai Pujitha Nallapati"
date: "27/11/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1a)

```{r}
#load data
df <- read.csv(file = "COVID19_cases_Toronto.csv")

df$Ever.Hospitalized <- ifelse(df$Ever.Hospitalized == 'Yes', 1,0)
# 1 == hospitalized
# 0 == not hospitalized
```

```{r}
mod1 <- glm(Ever.Hospitalized ~ Client.Gender+Age.Group, data = df, family = binomial)
summary(mod1)

```
##Interpret all the regression parameters

```{r}
# change the coefficients back into log ratios
round(exp(mod1$coefficients),2)
```
### Intercept
When the patient is in the age group 19 and younger and is a female, then the odds of not being hospitalized is greater by 100 times. 

### Client.GenderMale
Males have a 52.5% more odds of be hospitalized than Females.

### Age.Group20 to 29
Patients that lie in this age group have a slightly higher odds of not being hospitalized since 0.98 < 1. The odds ratios is within 5%, we can say there is negligible association between the events of yes or no hospitalization in this age group.


## To be completed....

1b)
```{r}
##Interaction between age and gender

mod2 = glm(Ever.Hospitalized ~ Age.Group + Client.Gender + Age.Group*Client.Gender, 
           data = df, family = binomial)
summary(mod2)

```
There are significant interactions between age and gender, therefore we will keep the interaction in the model. 

## 1c)
```{r}
round(exp(mod2$coefficients[18]),2)
```

When the patient is in the age group 90+ and is a male then the patient has a 92% more odds of being hospitalized.


1d)

```{r}
odds_inter_age_gender <- mod2$coefficients[11:18]

odds_inter_age_gender / (1 + odds_inter_age_gender)
```
## 1e)
```{r}
mod3 <- glm(Ever.Hospitalized ~ . + Age.Group * Client.Gender, 
            data=df, family="binomial")
summary(mod3)
```
Do not keep neighborhood and outbreaks since there is not a large difference in AIC, deviance, and AUC values. Not include the two categorical variables will ensure a less complex model with approximately the same performance.

### 1f) ROC Curve
```{r}
library(pROC)
p = predict(mod2, type = "response")
roc_logit = roc(df$Ever.Hospitalized~p) #AUC score

TPR = roc_logit$sensitivities

FPR = 1 - roc_logit$specificities

plot(FPR, TPR,
     xlim=c(0,1), ylim=c(0,1),
     type='l',lty=1, lwd=2,
     col='red',bty='n')

abline(a=0,b=1,lty=2,col='blue')
text(0.7,0.4, label=paste("AUC = ", round(auc(roc_logit),2)))
```


### 1g)

# TBD


## Question 2

### Part A

```{r}
# set parameters
set.seed(123)
n = nrow(df)
indexes <- c(1:n)
train_size = 0.60
predictors <- c("Outbreak.Associated", "Age.Group",
               "Neighbourhood.Name","Client.Gender") 
target <- c( "Ever.Hospitalized" )

# get sampled train and test indexes
train_index <- sample(indexes, n * train_size)
test_index <- indexes[ - train_index ]

# get train and test df
train_df <- df[train_index,]
test_df <- df[test_index,]
```

### Part B
```{r}
library(boot)

model_1 <- glm(Ever.Hospitalized ~ Age.Group + Client.Gender + Age.Group*Client.Gender, 
               data=df, family='binomial')

model_2 <- glm(Ever.Hospitalized ~ Age.Group + Client.Gender + Age.Group*Client.Gender + Neighbourhood.Name, 
               data=df, family='binomial')
```


```{r}
# ## Model calibration with cross-validation and bootstrap ##
# library(rms)
# 
# ## Fit the model with lrm from rms package ##
# lrm_1 <- lrm(Ever.Hospitalized ~ Age.Group + Client.Gender + Age.Group*Client.Gender, data=train_df,  x =TRUE, y = TRUE, model= T)
# cross.calib <- calibrate(lrm_1, method="crossvalidation", B=10) # model calibration
# 
# par(family = 'serif')
# plot(cross.calib, las=1, xlab = "Predicted Probability")

```


```{r}
# ## Fit the model with lrm from rms package ##
# lrm_2 <- lrm(Ever.Hospitalized ~ Age.Group + Client.Gender + Age.Group*Client.Gender + Neighbourhood.Name, data=train_df,  x =TRUE, y = TRUE, model= T)
# 
# cross.calib <- calibrate(lrm_2, method="crossvalidation", B=10) # model calibration

```


```{r}
total_cv_errors <-function(data, model_name, k=10){
  cv_errors = data.frame(delta1 = 0, delta2 = 0)
  for (i in 1:k){
  cv_errors[i, ] = cv.glm(data, model_name, K=k)$delta
  print(i)
}
  return(cv_errors)}

# http://www.science.smith.edu/~jcrouser/SDS293/labs/lab7-r.html
```

```{r}
m1_train_cv_errors <- total_cv_errors(train_df, model_1)
m1_test_cv_errors <- total_cv_errors(test_df, model_1)
```

```{r}
print(m1_train_cv_errors)
print(m1_test_cv_errors)
```

```{r}
m2_train_cv_errors <- total_cv_errors(train_df, model_2)
m2_test_cv_errors <- total_cv_errors(test_df, model_2)
```


```{r}
print(m2_train_cv_errors)
print(m2_test_cv_errors)
```